\documentclass[11 pt]{scrartcl}
\usepackage{tylercs}
\geometry{left=0.75in, top=0.75in, right=0.75in, bottom=0.8in}

\newcommand{\arttitle}{Social Choice Theory Overview}
\newcommand{\alphanum}{\begin{enumerate}[(a)]}
\newcommand{\enumend}{\end{enumerate}}
\newcommand{\BP}{\mathbf{P}}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[l]{\arttitle{}}
\fancyhead[r]{Tyler Zhu}
\cfoot{\thepage}

\begin{document}
\title{\Large \arttitle{}}
\author{\large Tyler Zhu}
\date{\large\today}
\maketitle

Thanks to Prof. Wes Holliday for his talk on Arrow's Theorem and Infinite Electorates, from which these notes are based on.

\section{Introduction}
\subsection{Profiles}
    Let $X$ (the alternatives) and $V$ (the voters) be nonempty sets. Let $O(X)$ be the set of strict weak orders on $X$.
    A $\textbf{profile}$ is a function $\mathbf{P}:ZV\to O(X)$.
    \begin{itemize}
        \ii Write $x\BP_i y$ for $\langle x,y\rangle \in \BP(i)$.
        \ii Let $\BP(x,y) = \{i\in V | x\BP_iy\}$.
        \ii Let $\BP_{|\{x,y\}}$ be the function mapping each $i\in V$ to $\BP(i) \cap \{x,y\}^2$.
    \end{itemize}

\subsection{SWFs}
A $\textbf{social welfare function}$ (SWF) is a function $f: O(X)^V \to O(X)$.
\begin{itemize}
    \ii Think of $f(\BP)$ as society's preference ranking, given the profile $\BP$ of individual preference rankings.
    \ii Write $xf(\BP)y$ for $\langle x,y\rangle \in f(\BP)$.
\end{itemize}

\section{Axioms}
\begin{itemize}
    \ii Universal Domain (UD)
    \begin{itemize}[-]
        \ii Idea: our SWF should work on any collection of ballots.
        \ii Formally: $\text{dom}(f)$ is the set of all profiles.
    \end{itemize}
    \ii Independence of Irrelevant Alternatives (IIA)
    \begin{itemize}[-]
        \ii Idea: the social preference for $x$ vs. $y$ shoudl depend only on how each voter ranked $x$ vs. $y$.
        \ii Formally: for any profiles $\BP$ and $\BP'$ such that $\BP_{|\{x,y\}} = \BP'_{|\{x,y\}}$:
        \[ xf(\BP)y \iff xf(\BP')y.\]
    \end{itemize}
    \ii Ranking (R)
    \begin{itemize}[-]
        \ii Idea: our voting system should yield a $\emph{ranking}$ of the candidates.
        \ii Formally: for any profile $\BP$, $f(\BP)$ is a strict weak order.
    \end{itemize}
    \ii Pareto (P)
    \begin{itemize}[-]
        \ii Idea: if every voter prefers $x$ to $y$, then society should prefer $x$ to $y$.
        \ii Formally: for any profile $\BP$ with $V\subseteq \BP(x,y)$, we have $xf(\BP)y$.
    \end{itemize}
    \ii Nondictatorship (ND)
    \begin{itemize}[-]
        \ii Idea: no one voter should have their way no matter how others vote.
        \ii Formally: there is no $i\in V$ such that for all profiles $\BP$, if $x\BP_iy$ then $xf(\BP)y$.
    \end{itemize}
\end{itemize}

The main results are the following.
\begin{theorem}[Arrow 1951]
    If $|X|\geq 3$ and $V$ is finite, then there is no SWF satisfying Universal Domain,
    Independence of Irrelevant Alternatives, Ranking, Pareto, and Nondictatorship.
\end{theorem}

\begin{theorem}[Fishburn 1970]
    If $V$ is infinite, then there is a SWF satisfying Universal Domain,
    Independence of Irrelevant Alternatives, Ranking, Pareto, and Nondictatorship.
\end{theorem}

\end{document}
